\documentclass{article}
\usepackage[cm]{fullpage}

\begin{document}
\title{\LARGE{\textsc{Capture The Flag}}\\\large{HacDC NARG}}
\maketitle
\section*{The Playing Field}
	\begin{itemize}
		\item Two teams of 10 players compete, Red and Blue.
		\item The playing field is a 50 by 50 unit plane centered on the origin, (0, 0, 0).
		\item Blue home-side is the negative side of the X-axis.
		\item Red home-side is on the positive side of the X-axis.
	\end{itemize}
\section*{Gameplay}
	\begin{itemize}
		\item If a player is tagged offsides, the player is sent to jail.
		\item If a player tags the jail on the other team's side, all of the jailed teammates are freed. The freed teammates are automatically zapped back to random locations on their home-side (``Free Walkbacks"). The agent that tagged the jail does not automatically return home.
		\item Agents cannot move their team's own flag.
		\item When the game starts, each flag is surrounded by a ``safe zone" in which offsides players cannot be tagged. This zone is static and vanishes once the flag is removed from the zone.
		\item The game is over when one of the following conditions has been met:
			\begin{itemize}
				\item One team's flag has been carried to the other team's side.
				\item All players from one team have been captured.
				\item 500 time units have elapsed.
			\end{itemize}
		\item The winning team is the team that:
			\begin{itemize}
				\item Captures the other team's flag.
				\item Captures all of the other team's players.
			\end{itemize}
	\end{itemize}
\section*{Tournament}
	\begin{itemize}
		\item There are five games in a tournament. 
		\item The winner of a tournament is the team that has won the most individual games in the tournament. 
	\end{itemize}
\section*{Agents}
	\begin{itemize}
		\item Agents have a maximum speed of 1.0 distance units per unit time.
		\item The agent's sensor range is 20 distance units.
	\end{itemize}
\section*{Technical Details}
	This part will come when I start messing with some security precautions and auto-tournament codes. 
\end{document}